\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{titlesec}
\usepackage{lmodern}
\usepackage{graphicx}
\usepackage{hyperref}

\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{}===
\titleformat{\subsection}{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\status{local}
\title^{\textbf{The Dimensional Field Theory}}
\author^{R.P.N. Esseling}
\version{1.0}
\maintainer^{R.P.N. Esseling}
\reviewer^{R.P.N. Esseling}
\copyright^{R.P.N Esseling}
\date{\today}

\collapse{browser}

\begin{document}

\maketitle

\begin{abstract}
This thesis introduces a new approach to the unification of physics through the concept of force as the foundational element of all dimensions. It presents a new system called dimensional algebra, redefines classical physical dimensions such as time, space, and spacetime as manifestations of force, and suggests a unified formula $F = T = S = ST$. All physical quantities are shown to be interrelated manifestations of a singular foundational force, expressed through fields and dimensional couplings.
\end{abstract}

\section{Introduction}

E = mc^2 or Emc^4^cmE or 2^mc = E 

Hereafter named F,T,S,and ST.

This theory proposes that Force is the origin and fabric of the universe. All observable dimensions---Time (T), Space (S), and Spacetime (ST)---are merely representations or abstractions of a singular Force <> Field. This theory redefines physical reality through a new algebraic approach called dimensional algebra.

\section{Dimensional Algebra Framework}

\subsection{Core Definitions}
\subsection{D = Dimension}
\begin{itemize}
    \item $F^0 = D_1$
    \item $F^0 = T^1 = D_2$
    \item $F^0 = T^1 = S^2 = D_3$
    \item $F^0 = T^1 = S^2 = ST^3 = D_4$
\end{itemize}

\noindent This suggests that each successive dimension emerges from force and its abstract representations and would with each emergence result in a new unidentified force. [$...?^4 = D_5$] or following the trend of 3's [$..S^2..ST^3 = ?^4 = D_5$] suggesting a shift in dimensions maintaining 3 dimensions one step upward if these exist.

\subsection{Unified Equation}
\[
F = T = S = ST
\]
This equation postulates that all forces are equal and interchangeable. Time, distance, and velocity are different expressions of the same universal force, making all unit systems fundamentally equivalent.

\section{Nature of Fields}
Each force is expressed as a field. F = Fi. A field has:
\begin{itemize}
    \item A parent field coupling
    \item Force as value (as opposing//imposing Force)
    \item A maximum Force value or collapse threshold
    \item A dimensional identity (T, S, ST)
    \item A possible frequency as Force stored at the molecular level
\end{itemize}

All fields are coupled with one another hierarchically, resulting in nested force systems creating balance and relativity. Relativity from top to bottom.

\section{Balance and Structure}
Balance is a natural phenomenon. For instance, Earth’s atmosphere is pressurized at 35 psi, its structure neatly divided into equal strata. Water boils at 3.5 psi, suggesting ratios of force as constants of transformation (10 minutes boil time as 35/3.5). Earth’s structure reflects this perfect balance. In our galaxy this balancing example would also show as gravitational Force of the sun, in that there are 24 Earths between the Earth and the Sun, giving the biggest the advantage, as Inertia's momentum (i.e. surface tension, escaping ground gravity) it would amount to 24 units of Gravitational Force. 

\section{Force Ratios and Field Collapses}
Field collapse is the replacement of a field with an equal field of higher Force.
The theory proposes collapses based on threshold ratios:
\begin{itemize}
    \item Field Force $\times$ 3.2 = Collapse Threshold at each stage (or F^1, F^2, F^3) relative to parent Field.
    \item Collapse stages: partial, half, full
\end{itemize}

\section{Field Force Magnification}
The theory proposes magnification of Force based on threshold ratios:
\begin{itemize}
    \item Each stage transition results in Force magnification in degrees of F^1,F^2, F^3. Or 3.2 times.
    \item A factor of 3 is always relevant in terms of Force increase as past F^3 a field would collapse fully and would in essence become it's parent in every way and not only force value). Resulting in hyperbolic increase in force. As much as the difference between child and parent in Force. 
\end{itemize}

A missile at Mach 27 may enter a higher dimensional state—leaving Time becoming phasing-dimensional.
Observant from invisibility of the missile. Only observable with frequency tracking. This was carried out by the American Air Force.

\section{Universal Constants and Derived Measurements}
\begin{itemize}
    \item Speed of light cubed yields universe size $\approx$ 54 billion light-years. T^1, S^2, ST^3.
    \item $\sqrt{\sqrt{Diameter}} = 32$ → Smallest field value observed ,and default sqrt of anything >9999(+1) even numbers in Diameter (balanced bigger matter) 
    \item {$32 => 3.2$} common denominator for Field Collapse force ratios.
    \item $\sqrt[32] = 0$ -> Remainder of 0 = 1. Truancy check for calculated S^2 Force values
    \item Field value's for planet form are N32 upwards to N33.000. Having threshold barriers at N33.000, N66.0000, N99.999 => Likely amounts to dimensional collapse. i.e. black hole. But it could be relative to it fields parent still, Predicting a minimum force for dimensional collapse  would be:
    F(32)^1, F(32)^2, F(32)^3 => N100.000(-1) 
\end{itemize}

\section{Limit of Force and Dimensional Constraint}
\begin{itemize}
	\item (F = F)^2. Suggesting deadlock or stalemate at this D^4 = ST or other dimensional level. Deadlock is absolute requirement for existence as Force is held up by Force, creating an infinity of momentum/reaction. Without deadlock, no balance and equilibrium. Evidence suggests space is pressurized. As pressure is falling and dynamic. Stalemate or deadlock could be evident in black hole vs. black hole(s) as barriers of the universe. Evidence of both is frequent and available through radioactive observation of galaxy (ring along all observations engrossing 66/100 of area => black hole at the center of universe, radioactive spotted blanket at observed other direction(s)).
	
	\item Force value suggest that all close observable objects seem to center around 32. The closer we look at the assumed black hole at the center of the universe the more we see that it more frequently uses 32 as it's centered value. Suggesting we are under the influence of it's Forces.  
	

\section{Experimental Observations}
\begin{itemize}
\item Collaborations with the Air Force on flight data suggested gravitational force compression at increasing aircraft speeds. Time dilation, field compression as increased hold (linear), and gravitational curvature (linear) were both at the same time observed as seismology blot responses—evidence of force field structure. With much appreciation they helped prove gravity was a field.
\item An M16 under full auto-fire would show a non-linear increase in fire power. Cutting down a bush at base level but would end up cutting cars in half. Highly suggested to be field collapse in advancing sequence.
\item A basin filled with salt-water and deminerialized water would create a faster reaction (by exchange of fields, per water type) than a single basin. Showing that reacted elements prefer other fields. If reacting with electrolysis the water would accept more salt as reaction and current increases. Evidence suggest water (as field) ignores it's water to salt ratio limit if the element of salt is reacting. The bound salt would bind to the electrolysis rod. Possibly suggesting yet undisclosed small-to-large element binding at the molecular level.
\item A fast or flash reaction is essentially a perfect execution of going through all the stages. Growing non-linear in Force and chasing after parent's parent field. Always getting hotter in ever increasing steps. Suggests that all reactions that produce heat are at the base of an example of the field collapse/expanse theory.

\section{Conclusion}
This unified theory redefines our understanding of the universe by postulating that all dimensions, fields, and phenomena emerge from a singular omnipresent force. Through dimensional algebra and field dynamics, a complete picture of reality is drawn in perfect balance.

\end{document}
\endcollapse
